---
title: "Problem Statement 5 Codes (AIC 2020)"
author: "CodingWarriors"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_depth: 4
    toc_float: 
      collapsed: TRUE
      smooth_scroll: FALSE
    number_sections: TRUE
    code_folding: show 
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#Importing relevant libraries
library(tidyverse)
library(pdftools)
library(xlsx)
library(tabulizer)
```

# Function to extract information 

We first define extract_info function to extract the relevant information from an invoice with a pre-defined search area. After which, we will conduct data wrangling and cleaning on the extracted data.
```{r}
#Defining function to extract Invoice values
extract_info <- function(invoice){

  area = list(c(196.9688, 31.6875, 248.5312, 580.3125)) #Search area extracted using tabulizer::locate_areas()
  
  raw_df <- extract_tables(
    invoice, pages = 1, area = area, 
    guess = FALSE, output = "data.frame"
  ) %>% 
    purrr::pluck(1)  %>%
    set_names(c("Company", "Invoice.Issue.Date", "Invoice.Number", "Total.Due")) 
  
   raw_df$Total.Due <- raw_df$Total.Due %>%
     map_chr(~trimws(gsub("\\$|,", "", .x)))
  
  result_df <- data.frame(Company = raw_df$Company[2], Invoice.Issue.Date = raw_df$Invoice.Issue.Date[1], Invoice.Number = raw_df$Invoice.Number[1], Total.Due = as.numeric(raw_df$Total.Due[2]))
  
  result_df
}

```

# Extracting information from all Invoices
We will then apply the function defined above to all of the invoices, storing all of the extracted data in a table format.
```{r}
invoices <- list.files() %>% .[grepl(".pdf", .)] 

invoices_df <- data.frame(Company = NA, Invoice.Issue.Date = NA, Invoice.Number = NA, Total.Due = NA)[numeric(0),]

#Apply extract_info function to all of the invoices
for (j in 1:length(invoices)) {
  invoices_df <- rbind(invoices_df,extract_info(invoices[j]))
}

invoices_df
```

# Analyzing Client's financial data 
The recorded financial data of the audit client is extracted for analysis to identify errors. 
```{r}
client_data <- read.xlsx("Client_Financial_Data.xlsx", 1)

client_data
```


# Output an excel file which contains errors in Client's financial data
The errors are then subsequently stored in a new excel file titled "Error_Summary.xlsx" for manual processing. The "No." columns represent the rows in the Client's financial data which contains error(s) (NA indicates missing records in Client's financial data).

```{r}
client_data$Total.Due <- client_data$Total.Due %>%
     map_chr(~trimws(gsub("\\$|,", "", .x))) %>%
  as.numeric()

combined_df <- full_join(
  anti_join(invoices_df, client_data, by = colnames(invoices_df)), 
  anti_join(client_data, invoices_df, by = colnames(invoices_df)), 
  by = colnames(invoices_df)
  ) 

rbind(
  combined_df %>%
    filter(Invoice.Number %in% distinct(.,Invoice.Number)[[1]] & !is.na(No.)), 
  combined_df %>%
    filter(!(Invoice.Number %in% client_data$Invoice.Number))
) %>%
  write.xlsx(., "Error_Summary.xlsx",sheetName="Errors", col.names=TRUE, row.names=FALSE, append=FALSE)

read.xlsx("Error_Summary.xlsx",sheetName="Errors")
```
